\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-01-23 papers/jss/article.Rnw
Section 6:
Add the oxford comma somewhere I missed it earlier.
Use \code{} instead of \texttt{} for a function name.


git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@838 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

The previous sections discussed functionality in the \pkg{RProtoBuf} package
for creating, manipulating, parsing and serializing Protocol Buffer
messages of a defined schema.  This is useful when there are
pre-existing systems with defined schemas or significant software
components written in other languages that need to be accessed from
within \proglang{R}.

The package also provides methods for converting arbitrary \proglang{R} data structures into protocol
buffers and vice versa with a universal \proglang{R} object schema. The \texttt{serialize\_pb} and \texttt{unserialize\_pb}
functions serialize arbitrary \proglang{R} objects into a universal Protocol Buffer 
message:

>>>>

The previous sections discussed functionality in the \pkg{RProtoBuf} package
for creating, manipulating, parsing, and serializing Protocol Buffer
messages of a defined schema.  This is useful when there are
pre-existing systems with defined schemas or significant software
components written in other languages that need to be accessed from
within \proglang{R}.
The package also provides methods for converting arbitrary \proglang{R} data structures into protocol
buffers and vice versa with a universal \proglang{R} object schema. The \code{serialize\_pb} and \code{unserialize\_pb}
functions serialize arbitrary \proglang{R} objects into a universal Protocol Buffer 
message:
